\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[colorinlistoftodos]{todonotes}
\title{Product Planning}

\usepackage{enumitem}
\usepackage{authblk}
\setlist{nolistsep}
\author[1]{Boudewijn van Groos}
\author[2]{Chris Langhout}
\author[3]{Jens Langerak}
\author[4]{Paul van Wijk}
\author[5]{Louis Gosschalk}

\affil[1]{bvangroos \\
	4229843}
\affil[2]{clanghout \\
	4281705}
\affil[3]{jlangerak \\
	4317327}
\affil[4]{pvanwijk \\
	4285034}
\affil[5]{lgosschalk \\
	4214528}


\date{\today}

\begin{document}
\maketitle
\begin{abstract}
	This document describes the product planning. It describes the requirements by using the MoSCoW method and by making use of user stories. Furthermore it gives a planning of the releases and it describes definition of done for the backlog items, sprints and releases.
\end{abstract}
\newpage
\tableofcontents
\newpage

\section{Introduction}
This document discusses the product planning. In the first section it describes the requirements according the MoSCoW method. Section \ref{subsec:User-stories} contains the user stories for some of the requirements. Furthermore this document contains the planning for the product. In section \ref{subsec: roadmap} there is a high-level overview of the roadmap and section \ref{subsec: release-plan} gives a detailed planning for each week. Section \ref{sec: Definition-of-Done} explains what the definition of done is for a backlog item, for a sprint and for a release. 
\section{Product}
This section describes the requirements of the product. It also contains a high-level roadmap.
\input{MoSCoW/moscow}
\input{roadmap}
\section{Product backlog}
\input{user-stories}
\input{release-plan}
\input{definition-of-done}



\end{document}