\subsection{Initial release plan}
\label{subsec: release-plan}
This section will describe the planning for the product. The release plan is based on sprints of one week. The numbers of the week correspond to the week of quarter 4. A new iteration starts on every Friday. For each week we will list which features the product should have and which additional task must be done.
\subsubsection{Week 4.1}
\begin{itemize}
	\item Setup the software that is used during the project.
	\item Obtain the requirements.
\end{itemize}

\subsubsection{Week 4.2}
\begin{itemize}
\item A basic architecture for the product.
\item A design for the user interface.
\item A draft version of the product vision.
\end{itemize}
\subsubsection{Week 4.3}
\begin{itemize}
	\item A minimal user interface according the design of week 4.2.
	\item The final version of the product vision.
	\item A draft version of the product planning.
	\item The user must be able to specify in a data description file how a file should be read by the program.
	\item The user must be able to specify which data must be written to a file.
	\item The user must be able to perform constraint analyses.
\end{itemize}
\subsubsection{Week 4.4}
\begin{itemize}
	\item The final version of the product planning.
	\item The user must be able the perform chunking analyses.
	\item The user must be able the perform connections analyses.
	\item The user must be able the perform computation analyses.
\end{itemize}
\subsubsection{Week 4.5}
\begin{itemize}
	\item The user must be able the perform codes analyses.
	\item The user must be able the perform comparisons analyses.
	\item It must be possible to show the data as frequency bars.
	\item It must be possible to show the data as a line graph.
\end{itemize}
\subsubsection{Week 4.6}
\begin{itemize}
	\item The user must be able the perform comments analyses.
	\item The user must be able the perform conversions analyses.
	\item It must be possible to show the data as a box plot.
	\item It must be possible to show the data as a Stem-and-Leaf plot.
	\item Input for SIG.
\end{itemize}
\subsubsection{Week 4.7}
\begin{itemize}
	\item It must be possible to show the data as a state transition matrix.
	\item Show the data with Lag analysis
	\item The user must be able to export the visualizations as an image.
	\item It must be possible to show the data as a Histogram.
\end{itemize}
\subsubsection{Week 4.8}
\begin{itemize}
	\item It must be possible to show the data as a Markov chain.
	\item Specify multiple files that all will be analyzed individually.
	\item Implement certain analyses functions in our language.
\end{itemize}
\subsubsection{Week 4.9}
	This is the last week where it is possible to work on the code. This week will add no new features. In this way we will be able to handle some delay during the process. Furthermore this week is used to repair the last bugs. Therefore there is a feature freeze on Wednesday June 17. 
\begin{itemize}
	\item Final input for SIG
	\item Draft version of the final report
\end{itemize}
\subsubsection{Week 4.10}
\begin{itemize}
	\item Final report
	\item Product presentation
\end{itemize}