\subsection{User stories}
\label{subsec:User-stories}
This section describes some user stories. The user stories are based on the requirements as described in section \ref{subsec: MoSCoW}. Each user story answers the questions who, what and why. The stories follow the following template "As a $who$, I want $what$, so that $why$". The user stories are sorted on priority. The stories at the start have a high priority and the stories at the end have a low priority.
\subsubsection{Must Haves}
As a user, I want to be able to specify the analysis I want to perform, so that I get relevant results from the program. 
\\\\
As a user, I want to be able to load the data that should be analyzed in the program, so that the analysis is performed over relevant data. 
\\\\
As a user, I want to be able to specify which columns contain dates and in what format the dates are, so that I can perform analysis based on the date.
\\\\
As a user, I want to be able to specify which columns are numeric, so that I can perform analyses based on numeric values
\\\\
As a user, I want to be able to specify the name of the data columns, so that I can use those names in the analysis.
\\\\
As a user, I want to be able to create a file that specifies which files should be read for the data, so that I can load multiple files at once.
\\\\
As a user, I want to be able to specify the relation between different data files, so that I can use multiple files in an analyses.
\\\\
As a user, I want to be able write the output of an analysis to a file, so that I can use the result for further analysis.
\\\\
As a user, I want to be able to specify which columns should be written to a file, so that I can discard non relevant data.
\\\\
As a user I want to be able to view the data as Frequency bars, so that I can see how often an event happens.
\\\\
As a user, I want to be able to view the data as a Line Graph, so that I can see how the behavior of the analyzed person changes over time.
\\\\
As a user, I want to have a manual that specifies the languages that is used for analyses.

\subsubsection{Should Haves}
As a user, I want to be able to export a visualization as an image, so that I can use the image in reports.
\\\\
As a user I want to be able to view the data as a Box plot, so that I can see how the data is distributed.

\subsubsection{Could Haves}
As a user, I want to be able to perform one analysis over multiple datasets, so that I can perform the same analysis over all statsensors at once.
\\\\
As a user, I want to be able to edit an analysis in the program, so that I don't have to reload the analysis when I change it.
\\\\
As a user, I want to preview the output of an analysis, so that I immediately can see if the result is what I expected.
