In our language we support many operations on numbers and booleans.

For numbers we support:
\begin{itemize}
	\item $+$
	\item $-$
	\item $*$
	\item $/$
	\item $^\wedge$
	\item $\%$
	\item $SQRT$
	\item $>$
	\item $<$
	\item $<=$
	\item $>=$
\end{itemize}

For booleans we support:
\begin{itemize}
	\item $AND$
	\item $OR$
	\item $NOT$
\end{itemize}

All values support the equality operation $=$.

\subsection{Date operations}
To operate on dates we have several functions which can be called.

\subsubsection{Relative}
In order to work more freely with dates we support the RELATIVE function. This functions calculates the differences between 2 dates in a given time unit.

For example:
$RELATIVE(\#1995-01-17\#, \#2015-06-18\#, DAYS)$ \\
Gives the result $7457$.

The first 2 arguments are the dates to compare and the third argument is the unit. The supported units are DAYS, MONTHS and YEARS.

\subsubsection{Combine}
The combine function combines a date and a time to give a date time.

For example:
$COMBINE(\#1995-01-17\#, \#12:12\#)$ \\
Returns the equivalent of $\#1995-01-17\ 12:12\#$.

The first argument is the date and the second the time.

\subsubsection{To date and To time}
To get either the time part or date part of a given date time you can call TO\_DATE or TO\_TIME.

For example:
$COMBINE(TO\_DATE(\#1995-01-17\ 12:12\#), TO\_TIME(\#1995-01-17\ 12:12\#))$ \\
Results in $\#1995-01-17\ 12:12\#$ and is a rather useless operation.

TO\_DATE and TO\_TIME both only take one date time argument.

\subsubsection{After and Before}
To compare dates we have the BEFORE and AFTER operations.

For example:
$\#1995-01-17\#\ BEFORE\ \#1995-01-18\#$ \\
Results in true.

All different temporal values are supported, so BEFORE and AFTER work with times, dates and date times. Do note: that mixing only works between dates and date times. Since $\#1995-01-17\#\ BEFORE\ \#12:00\#$ is nonsense.

\subsubsection{Add and Min}
To add or subtract time we support the ADD and MIN operations.

For example:
$\#1995-01-17\#\ ADD\ \#1\ YEARS\#$ \\
Results in $\#1996-01-17\#$.

The left side argument should either be a date or a date time and the right side argument should be a period. The supported units are DAYS, MONTHS and YEARS.