\chapter{Outlook} %MAX 1 PAGE

Our product is finished for this course. It satisfies all the crucial needs of the customer and even covers some additional non-crucial desires. Though, if our software were to be used by a more broad range of customers in the future, a couple of changes should be made to make the software usable for more than just the ADMIRE analysts.

\section{Improvements}
Certain improvements would be advisable to make the software usable to a broad crowd of analysts. For example, when rescaling the main window of the program, the text fields do not adjust accordingly. This is an improvement which is not at all necessary but is a great improvement to the usability of the product. Another important improvement would be to do more extensive testing and thus solving more bugs, since a broader crowd means a more varying set of customers and thus requires a more robust, solid software.

Our software has been created with the aim to assist the ADMIRE analysts, but in the process we decided to keep the language rather generic. This means our analysis language is already quite suitable for a larger audience than just the ADMIRE analysts. A possible addition to the language would be a way to generate visualizations without having to generate the table and to create the visualization in the separate tab for this. This would improve the usability because it reduces the required steps for a user to do visualizations when they do not explicitly want to see the result data in a table.

Another feature which would come in handy is to be able to export into excel format. A lot of analysts appear to be working with excel and excel files can of course also be loaded into SPSS and other analysis tools, so adding this feature would surely not be a waste of effort for the product quality.

\section{Future Development}
Assuming we win an award and continuation of development becomes interesting, we will most likely continue in the same way we are working now. Though, probably without the daily get togethers. We will most likely have multiple virtual meetings weekly to discuss the scrum progress and set some weekly goals to accomplish. This way we can combine the development with the daily lives of all members.